Hilbert space approximate Bayesian Gaussian processes using Stan

### 2020-04-10 Paper/manuscript_v2/manuscript_07_01.tex
hyperref colors

\usepackage[colorlinks=true]{hyperref}

@@

\author{Gabriel Riutort-Mayol$^{1*}$, Paul-Christian Bürkner$^2$, Michael R. Andersen$^{3}$, Aki Vehtari$^{2}$}

@@

\begin{figure}
\centering
\begin{tabular}{ c c c }
\arrayrulecolor{darkgray}\hline
c = 1.05 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part1.pdf}
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part1.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part1.pdf} & 
\multirow{32}{1cm}{ \includegraphics[scale=0.35, trim = 28mm 30mm 100mm 30mm, clip]{ch5_fig3_legend.pdf}}\\ 
\arrayrulecolor{lightgray}\cline{1-2}
c = 1.1 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part2.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part2.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part2.pdf} &\\
\cline{1-2}
c = 1.2 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part3.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part3.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part3.pdf} &\\
\cline{1-2}
c = 1.5 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part4.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part4.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part4.pdf} & \\
\cline{1-2}
c = 2 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part5.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part5.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part5.pdf} & \\
\cline{1-2}
c = 2.5 &
\includegraphics[scale=0.215, trim = 0mm 4mm 0mm 14mm, clip]{ch5_fig3_Post_part6.pdf}
\includegraphics[scale=0.215, trim = 0mm 4mm 0mm 14mm, clip]{ch5_fig3_Sigma_part6.pdf}
\includegraphics[scale=0.215, trim = 0mm 4mm 5mm 14mm, clip]{ch5_fig3_Cov_part6.pdf} &\\
\arrayrulecolor{darkgray}\hline
\end{tabular}
\caption{Posterior mean predictive functions (left), covariance functions (center) and posterior standard deviations (right) of both the exact GP model and the HSGP model for different number of basis functions $m$ and for different values of the boundary factor $c$. The dashed red line of the exact GP can hardly be seen in the some of the plots because it is under the blue lines.}
  \label{fig3_Post_part1}
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.42, trim = 10mm 100mm 5mm 30mm, clip]{ch5_fig7_legend.pdf}}\\
\vspace{-3mm}
\subfigure{\includegraphics[scale=0.31, trim = 1mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part1.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part2.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part3.pdf}}\\
\vspace{-3mm}
\subfigure{\includegraphics[scale=0.31, trim = 1mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part4.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part5.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part6.pdf}}\\
\vspace{-3mm}
\subfigure{\includegraphics[scale=0.31, trim = 1mm 5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part7.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part8.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part9.pdf}}\\
\vspace{-3mm}
\caption{Mean posterior predictions of both exact GP and HSGP models, fitted over various datasets drawn from square exponential GP models with different characteristic lengthscales ($\ell$) and same marginal variance ($\alpha$) as the data-generating functions (\textit{true function}). The dashed red line of the exact GP can hardly be seen in the plots because it is almost perfectly overlayed by the blue lines.}
  \label{fig7_posterior_varing_lscale_part1}
\end{figure}

>>>>

\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=black]{hyperref}

@@

\author{Gabriel Riutort-Mayol$^{1*}$, Paul-Christian Bürkner$^2$, Michael R. Andersen$^{3}$,\\
 Aki Vehtari$^{2}$, Arno Solin$^{2}$}

@@

\begin{figure}
\centering
\begin{tabular}{ c c c }
\arrayrulecolor{darkgray}\hline
c = 1.05 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part1.pdf}
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part1.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part1.pdf} & 
\multirow{32}{1cm}{ \includegraphics[scale=0.35, trim = 28mm 30mm 100mm 30mm, clip]{ch5_fig3_legend.pdf}}\\ 
\arrayrulecolor{lightgray}\cline{1-2}
c = 1.1 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part2.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part2.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part2.pdf} &\\
\cline{1-2}
c = 1.2 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part3.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part3.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part3.pdf} &\\
\cline{1-2}
c = 1.5 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part4.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part4.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part4.pdf} & \\
\cline{1-2}
c = 2 &
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Post_part5.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 0mm 14mm, clip]{ch5_fig3_Sigma_part5.pdf} 
\includegraphics[scale=0.215, trim = 0mm 14mm 5mm 14mm, clip]{ch5_fig3_Cov_part5.pdf} & \\
\cline{1-2}
c = 2.5 &
\includegraphics[scale=0.215, trim = 0mm 4mm 0mm 14mm, clip]{ch5_fig3_Post_part6.pdf}
\includegraphics[scale=0.215, trim = 0mm 4mm 0mm 14mm, clip]{ch5_fig3_Sigma_part6.pdf}
\includegraphics[scale=0.215, trim = 0mm 4mm 5mm 14mm, clip]{ch5_fig3_Cov_part6.pdf} &\\
\arrayrulecolor{darkgray}\hline
\end{tabular}
\caption{Posterior mean predictive functions (left), covariance functions (center) and posterior standard deviations (right) of both the exact GP model and the HSGP model for different number of basis functions $m$ and for different values of the boundary factor $c$. %The dashed red line of the exact GP can hardly be seen in the some of the plots because it is under the blue lines.
}
  \label{fig3_Post_part1}
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.42, trim = 10mm 100mm 5mm 30mm, clip]{ch5_fig7_legend.pdf}}\\
\vspace{-3mm}
\subfigure{\includegraphics[scale=0.31, trim = 1mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part1.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part2.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part3.pdf}}\\
\vspace{-3mm}
\subfigure{\includegraphics[scale=0.31, trim = 1mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part4.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part5.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 25.5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part6.pdf}}\\
\vspace{-3mm}
\subfigure{\includegraphics[scale=0.31, trim = 1mm 5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part7.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part8.pdf}}
\subfigure{\includegraphics[scale=0.31, trim = 21mm 5mm 10mm 19mm, clip]{ch5_fig7_posterior_varing_lscale_part9.pdf}}\\
\vspace{-3mm}
\caption{Mean posterior predictions of both exact GP and HSGP models, fitted over various datasets drawn from square exponential GP models with different characteristic lengthscales ($\ell$) and same marginal variance ($\alpha$) as the data-generating functions (\textit{true function}). %The dashed red line of the exact GP can hardly be seen in the plots because it is almost perfectly overlayed by the blue lines.
}
  \label{fig7_posterior_varing_lscale_part1}
\end{figure}
